Web Service Wrapping, Discovery and Consumption --- More Power to the End-User

### 2010-06-15 trunk/papers/icsoc2010/paper_sec_catalogue.tex
minor change
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@882 d8b0c59b-6544-0410-94d9-83a5658a058e

The persistence layer provides an API allowing to work with a standard set of objects representing the model. The interaction with the underlying RDF store is made via RDF2Go, an abstraction over triple (and quad) stores, which allows to program against rdf2go interfaces and choose any the RDF store implementation. This allows having a completely extensible and configurable framework for storage mechanisms, inferencers, RDF file formats, query result formats and query languages.

>>>>

The persistence layer provides an API allowing to work with a standard set of objects representing the model. The interaction with the underlying RDF store is made via RDF2Go, an abstraction over triple (and quad) stores, which allows to program against rdf2go interfaces and choose any RDF store implementation. This allows having a completely extensible and configurable framework for storage mechanisms, inferencers, RDF file formats, query result formats and query languages.
